

\section{Sustainable development in DCs?}


\subsection{The Question}

\begin{frame}{Week Question}{}

In developing countries, is sustainable development a way of overcoming limits to growth?

\mycomment{Tricky question, many assumptions. Not just yes/no, even with backup.
Before answering any question one should take
care of terms and assumptions}

  \begin{description}
  \item [sustainable development] an ambiguous term
		    \mycomment{We will start dealing with this, showing ambiguity and
		    providing a short genealogy of the term (its history)}
		    
  \item [a way of overcoming?] a silent casual link
		    \mycomment{this narrows the meaning of SD to a green version.
		    }
      
  \item [limits to growth?] are there hardwired limits? have we hit them?
		    \mycomment{}
		   
 	      
  \end{description}
\end{frame}


\section{What is Sustainable Development (SD)?}

\subsection{Historical lineages of SD}

\begin{frame}{Historical Context}{Pre-SD}
  \mycomment{Sorry to skip any further comments on 2001. 
  
	    {\bf Crisis of accumulation and governability/governance.}}

  \begin{description}
  
    \item [Pre-SD] The neoclassical development era.\\
	    No recognition of physical constraints.\\
	    Externalities
    \item [Limits to growth] hit the mainstream, the alarmist story of human destruction 
    \item [Overpopulation] the problem of a booming population: the Neo-Malthusian Perspective
    \item [Natural resource depletion] {\em Limits to Growth}(1972) perspective

  \end{description}
\end{frame}  


\subsection{Sustainable Development}
\begin{frame}{Sustainable Development}{Premises and definitions}

\begin{itemize}
\item Definition(s) ``Mainstream'' (adopted by World Commission on Environment and Development, World Bank etc.):
 
\begin{quotation}
SD is development that meets the needs of the present without
compromising the ability of the future generations to meet their own needs (Lele 1991, 611)
\end{quotation}

 \item  Premises
 
 
  \begin{enumerate}
   \item Ecological limits exist to growth
   \item Environmental degradation and poverty (Lele 1991) 
   \item Importance of traditional development goals
  \end{enumerate}
  
  

\end{itemize}
 
\end{frame}


\begin{frame}{Sustainable Development}{Objectives}
\begin{itemize}
 \item reviving growth
 \item changing the quality of growth
 \item meeting essential needs for jobs, food, energy, water and sanitation
 \item ensuring a sustainable level of population
 \item conserving and enhancing the resource base
 \item reorienting technology and managing risk
 \item merging environment and economics in decision making
 \item reorienting international economic relations
 \item making development more participatory
\end{itemize}

\end{frame}

